Ground state energy of quantum dots using the coupled cluster method

### 2018-06-04 project_2/article/article.tex
Thorough intermediate computation in appendix.

		Now comes the rather tedious task of evaluating all the terms 
		that arises from inserting \autoref{eq:normal_order_expansion}
		into \autoref{eq:doubles_amplitude_1}. This can be done by applying
		Wick's generalised theorem, but the task is a daunting and streneous one.
		A few example computations of how this can be done is included in
		\autoref{app:wickOnAmplitude}.
	 	Instead of doing it in this manner, we employ the second quantisation library
	 	from SymPy instead\footnote{This is also more in the spirit of this project,
	 	as it is within the realm of \emph{Computational} Physics.}.
		The CCD amplitude equation, from SymPy computation, is 
		\begin{equation}
		\begin{aligned}
			0 =& u^{ab}_{ij} + f^b_c t^{ac}_{ij}P(ab) - f^k_jt^{ab}_{ik}P(ij) \\
				 +& \frac{1}{4}t^{cd}_{ij} t^{ab}_{mn} u^{mn}_{cd} + \frac{1}{2}t^{cd}_{ij} u^{ab}_{cd} \\
				 +& \frac{1}{2}t^{cd}_{jm} t^{ab}_{in} u^{mn}_{cd} P(ij) - \frac{1}{2}t^{ac}_{nm} t^{bd}_{ij} u^{nm}_{cd} P(ab) \\
				 +& t^{ac}_{im} t^{bd}_{jn} u^{mn}_{cd} P(ij) + t^{ac}_{im} u^{bm}_{jc} P(ab) P(ij) \\
				 +& \frac{1}{2}t^{ab}_{mn} u^{mn}_{ij}. 
		\label{eq:CCD_amp_1}
		\end{aligned}
		\end{equation}

@@

		The we can define a new function consisting of all of \autoref{eq:CCD_amp_1} 
		except term number two and three,
		\begin{equation}
		\begin{aligned}		
			g(u, \tau) =&
					u^{ab}_{ij} + \tilde{f}^b_c t^{ac}_{ij}P(ab) - \tilde{f}^k_jt^{ab}_{ik}P(ij) \\
				 +& \frac{1}{4}t^{cd}_{ij} t^{ab}_{mn} u^{mn}_{cd} + \frac{1}{2}t^{cd}_{ij} u^{ab}_{cd} \\
				 +& \frac{1}{2}t^{cd}_{jm} t^{ab}_{in} u^{mn}_{cd} P(ij) - \frac{1}{2}t^{ac}_{nm} t^{bd}_{ij} u^{nm}_{cd} P(ab) \\
				 +& t^{ac}_{im} t^{bd}_{jn} u^{mn}_{cd} P(ij) + t^{ac}_{im} u^{bm}_{jc} P(ab) P(ij) \\
				 +& \frac{1}{2}t^{ab}_{mn} u^{mn}_{ij}, 
		\end{aligned}
		\end{equation}

		where $\tilde{t}$ are the non-diagonal parts of the Fock matrix.

@@

		\subsubsection{Intermediate Computations}
		Looking closely at the amplitude equation in (\ref{eq:CCD_amp_1}) one might come
		to realize that it contains that this equation contains many of the same structures in
		several of the terms. This warrants the search for an algebraic transformation of the
		CCD amplitude equation that has the potential to reduce the amount of floating point
		operations needed to compute it. As it turns out, such terms exist and they will decrease
		the computing time necessary by an order of magnitude. We will define the following
		"intermediates",
		\begin{align}
			 \chi^{ab}_{cd} &= \frac{1}{4}t^{ab}_{mn} u^{mn}_{cd} + \frac{1}{2}u^{ab}_{cd} \\
    			 \chi^a_d &= \frac{1}{2} t^{ac}_{nm} u^{nm}_{cd} \\
   			 \chi^{bm}_{jc} &= u^{bm}_{jc} + \frac{1}{2}t^{bd}_{jn}u^{mn}_{cd} \\
    			 \chi^n_j &= \frac{1}{2}t^{cd}_{jm} u^{mn}_{cd}.
		\end{align}
		These intermediate structures will allow us to rewrite \autoref{eq:CCD_amp_1} to,
		THIS REMAINS TO BE CHECKED!! 
		\begin{equation}
		\begin{aligned}
			0 =& \frac{1}{2}t^{ab}_{mn}u^{mn}_{ij} - t^{ab}_{im}u^{mn}_{jn}P(ij)
      		+ t^{cd}_{ij}\chi^{ab}_{cd} - t^{bd}_{ij}\chi^a_d P(ab) \\
      	  &+ t^{ac}_{im}\chi^{bm}_{jc}P(ab)P(ij)
      		+ t^{ab}_{in}\chi^n_jP(ij) + u^{ab}_{ij}.
		\end{aligned}
		\end{equation}
		The importance of this "trick" will become apparent in due time.

@@

>>>>

		Now comes the rather tedious task of evaluating all the terms 
		that arises from inserting \autoref{eq:normal_order_expansion}
		into \autoref{eq:doubles_amplitude_1}. This can be done by applying
		Wick's generalised theorem, but the task is a daunting and streneous one.
		A few example computations of how this can be done is included in
		\autoref{app:wickOnAmplitude}.
	 	Instead of doing it in this manner, we employ the second quantisation library
	 	from SymPy instead\footnote{This is also more in the spirit of this project,
	 	as it is within the realm of \emph{Computational} Physics.}.
		The CCD amplitude equation, from SymPy computation, is 
		\begin{equation}
		\begin{aligned}
			0 =& u^{ab}_{ij} + f^b_c t^{ac}_{ij}P(ab) - f^k_jt^{ab}_{ik}P(ij) \\
				 +& \frac{1}{4}t^{cd}_{ij} t^{ab}_{mn} u^{mn}_{cd} + \frac{1}{2}t^{cd}_{ij} u^{ab}_{cd} \\
				 +& \frac{1}{2}t^{cd}_{jm} t^{ab}_{in} u^{mn}_{cd} P(ij) - \frac{1}{2}t^{ac}_{nm} t^{bd}_{ij} u^{nm}_{cd} P(ab) \\
				 +& t^{ac}_{im} t^{bd}_{jn} u^{mn}_{cd} P(ij) + t^{ac}_{im} u^{bm}_{jc} P(ab) P(ij) \\
				 -& \frac{1}{2}t^{ab}_{im} u^{mn}_{jn}. 
		\label{eq:CCD_amp_1}
		\end{aligned}
		\end{equation}

@@

		The we can define a new function consisting of all of \autoref{eq:CCD_amp_1} 
		except term number two and three,
		\begin{equation}
		\begin{aligned}		
			g(u, \tau) =&
					u^{ab}_{ij} + f^b_c t^{ac}_{ij}P(ab) - f^k_jt^{ab}_{ik}P(ij) \\
				 +& \frac{1}{4}t^{cd}_{ij} t^{ab}_{mn} u^{mn}_{cd} + \frac{1}{2}t^{cd}_{ij} u^{ab}_{cd} \\
				 +& \frac{1}{2}t^{cd}_{jm} t^{ab}_{in} u^{mn}_{cd} P(ij) - \frac{1}{2}t^{ac}_{nm} t^{bd}_{ij} u^{nm}_{cd} P(ab) \\
				 +& t^{ac}_{im} t^{bd}_{jn} u^{mn}_{cd} P(ij) + t^{ac}_{im} u^{bm}_{jc} P(ab) P(ij) \\
				 -& \frac{1}{2}t^{ab}_{im} u^{mn}_{jn}.
		\end{aligned}
		\end{equation}

		where $\tilde{f}$ are the non-diagonal parts of the Fock matrix.

@@

		\subsubsection{Intermediate Computations}
		Looking closely at the amplitude equation in (\ref{eq:CCD_amp_1}) one might come
		to realize that it contains that this equation contains many of the same structures in
		several of the terms. This warrants the search for an algebraic transformation of the
		CCD amplitude equation that has the potential to reduce the amount of floating point
		operations needed to compute it. As it turns out, such terms exist and they will decrease
		the computing time necessary by an order of magnitude. We will define the following
		"intermediates",
		\begin{align}
            \chi^{ab}_{cd} &= \frac{1}{4}t^{ab}_{mn} u^{mn}_{cd} + \frac{1}{2}u^{ab}_{cd} \\
            \chi^n_j &= \frac{1}{2}t^{cd}_{jm} u^{mn}_{cd} \\
            \chi^a_d &= \frac{1}{2} t^{ac}_{nm} u^{nm}_{cd} \\
            \chi^{bm}_{jc} &= u^{bm}_{jc} + \frac{1}{2}t^{bd}_{jn}u^{mn}_{cd} 
		\end{align}
		These intermediate structures will allow us to rewrite \autoref{eq:CCD_amp_1} to,
		\begin{equation}
		\begin{aligned}
            0 =& u^{ab}_{ij} + f^b_c t^{ac}_{ij}P(ab) - f^k_jt^{ab}_{ik}P(ij) \\
              &+ t^{cd}_{ij}\chi^{ab}_{cd} + t^{ab}_{in}\chi^n_jP(ij) 
               - t^{bd}_{ij}\chi^a_dP(ab) \\ 
              &+ t^{ac}_{im}\chi^{bm}_{jc}P(ab)P(ij) + \frac{1}{2}t^{ab}_{im}u^{mn}_{jn}.
        \end{aligned}
	    \end{equation}
		The importance of this "trick" will become apparent in due time.

@@

\section{Finding Amplitude Equation Intermediates}     
    Starting from the CCD amplitude equation we factor out terms that will have the same
    indices if we contract them,
        &\begin{aligned}
        0 =& u^{ab}_{ij} + f^b_c t^{ac}_{ij}P(ab) - f^k_jt^{ab}_{ik}P(ij) \\
		  &+ \frac{1}{4}t^{cd}_{ij} t^{ab}_{mn} u^{mn}_{cd} + \frac{1}{2}t^{cd}_{ij} u^{ab}_{cd} \\
		  &+ \frac{1}{2}t^{cd}_{jm} t^{ab}_{in} u^{mn}_{cd} P(ij) - \frac{1}{2}t^{ac}_{nm} t^{bd}_{ij} u^{nm}_{cd} P(ab) \\
		  &+ t^{ac}_{im} t^{bd}_{jn} u^{mn}_{cd} P(ij) + t^{ac}_{im} u^{bm}_{jc} P(ab) P(ij) \\
		  &+ \frac{1}{2}t^{ab}_{im} u^{mn}_{jn},            
        \end{aligned}\\
        &\begin{aligned}
        0 =& u^{ab}_{ij} + f^b_c t^{ac}_{ij}P(ab) - f^k_jt^{ab}_{ik}P(ij) \\
		  &+ t^{cd}_{ij} \left(\frac{1}{4}t^{ab}_{mn} u^{mn}_{cd} + \frac{1}{2} u^{ab}_{cd} \right) \\
          &+  t^{ab}_{in} \left(\frac{1}{2} t^{cd}_{jm} u^{mn}_{cd}\right) P(ij) \\
          &- t^{bd}_{ij} \left(\frac{1}{2}t^{ac}_{nm}  u^{nm}_{cd}\right) P(ab) \\
          &+ \frac{1}{2}t^{ac}_{im} t^{bd}_{jn} u^{mn}_{cd} P(ij) - \frac{1}{2}t^{bc}_{im} t^{ad}_{jn} u^{mn}_{cd} P(ij)\\
          &+ t^{ac}_{im} u^{bm}_{jc} P(ab) P(ij) \\
		  &+ \frac{1}{2}t^{ab}_{im} u^{mn}_{jn}
        \end{aligned} \\
        &\begin{aligned}
        0 =& u^{ab}_{ij} + f^b_c t^{ac}_{ij}P(ab) - f^k_jt^{ab}_{ik}P(ij) \\
		  &+ t^{cd}_{ij} \left(\frac{1}{4}t^{ab}_{mn} u^{mn}_{cd} + \frac{1}{2} u^{ab}_{cd} \right) \\
          &+  t^{ab}_{in} \left(\frac{1}{2} t^{cd}_{jm} u^{mn}_{cd}\right) P(ij) \\
          &- t^{bd}_{ij} \left(\frac{1}{2}t^{ac}_{nm}  u^{nm}_{cd}\right) P(ab) \\
          &+ \frac{1}{2}t^{ac}_{im} t^{bd}_{jn} u^{mn}_{cd} P(ab) P(ij) \\ 
          &+ t^{ac}_{im} u^{bm}_{jc} P(ab) P(ij) \\
		  &+ \frac{1}{2}t^{ab}_{im} u^{mn}_{jn}
        \end{aligned} \\
        &\begin{aligned}
        0 =& u^{ab}_{ij} + f^b_c t^{ac}_{ij}P(ab) - f^k_jt^{ab}_{ik}P(ij) \\
		  &+ t^{cd}_{ij} \left(\frac{1}{4}t^{ab}_{mn} u^{mn}_{cd} + \frac{1}{2} u^{ab}_{cd} \right) \\
          &+  t^{ab}_{in} \left(\frac{1}{2} t^{cd}_{jm} u^{mn}_{cd}\right) P(ij) \\
          &- t^{bd}_{ij} \left(\frac{1}{2}t^{ac}_{nm}  u^{nm}_{cd}\right) P(ab) \\
          &+ t^{ac}_{im}\left(\frac{1}{2} t^{bd}_{jn} u^{mn}_{cd} + u^{bm}_{jc} \right)P(ab) P(ij) \\
		  &+ \frac{1}{2}t^{ab}_{im} u^{mn}_{jn}.
    Now we can introduce the intermediate $\chi$-terms,
        \chi^{ab}_{cd} &= \frac{1}{4}t^{ab}_{mn} u^{mn}_{cd} + \frac{1}{2}u^{ab}_{cd} \\
        \chi^n_j &= \frac{1}{2}t^{cd}_{jm} u^{mn}_{cd} \\
        \chi^a_d &= \frac{1}{2} t^{ac}_{nm} u^{nm}_{cd} \\
        \chi^{bm}_{jc} &= \frac{1}{2}t^{bd}_{jn}u^{mn}_{cd} + u^{bm}_{jc},  
    this gives us,
            0 =& u^{ab}_{ij} + \tilde{f}^b_c t^{ac}_{ij}P(ab) - \tilde{f}^k_jt^{ab}_{ik}P(ij) \\
              &+ t^{cd}_{ij}\chi^{ab}_{cd} + t^{ab}_{in}\chi^n_jP(ij) 
               - t^{bd}_{ij}\chi^a_dP(ab) \\ 
              &+ t^{ac}_{im}\chi^{bm}_{jc}P(ab)P(ij) + \frac{1}{2}t^{ab}_{im}u^{mn}_{jn}.
